---
title: "README"
author: "Bob Rudis"
date: January 06, 2016
output:
  md_document:
    variant: markdown_github
---

pluralize : Pluralize and Singularize Any Word

Based on the [pluralize.js](https://github.com/blakeembrey/pluralize) javascript library by Blake Embrey.

The following functions are implemented:

- `add_irregular_rule` :	Add a custom rule for making "deregularizing" a word
- `add_plural_rule` :	Add a custom rule for making a word plural
- `add_singular_rule` :	Add a custom rule for making a word singular
- `add_uncountable_rule` :	Make a word "uncountable"
- `pluralize` :	Pluralize and Singularize Any Word
- `singularize` :	Singularize a word

### News

- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/pluralize")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(pluralize)

# current verison
packageVersion("pluralize")

pluralize('test')
singularize('test')
pluralize('test', 5)
pluralize('test', 5, TRUE)
pluralize('regex')
add_plural_rule("gex", "gexii")
pluralize('regex')
singularize('singles')
add_singular_rule("singles", "singular")
singularize('singles')
pluralize("irregular")
add_irregular_rule("irregular", "regular")
pluralize("irregular")
pluralize("paper")
add_uncountable_rule("paper")
pluralize("paper")
```

### Test Results

```{r}
library(pluralize)
library(testthat)

date()

test_dir("tests/")
```

