---
title: "Why 'pluralize'\\?"
author: "Bob Rudis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Why pluralize\\?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
There are times when one needs to do some lightweight text mining and need to normalize words without the baggage that comes along with dependencies such as `tm` or `OpenNLP`.

One of the steps in this normalization process that is often helpful is to take plural words and make them singular vs "stem" them (which often leaves _interesting_ prefixes that work but aren't exactly "pretty".)

The English language makes this a bit more gnarly at times and there are also cases where one might want to bend the rules a bit (i.e. discipline-specific terminology that may not abide by the rules).

While many words can be made plural by just adding an "`s`" there are cases where one has to add "es", "ies" depending on the ending consonant or vowel.

There are further cases, like "`knife`", where there are special rules that force you to do things like make that "`knives`" to get the plural form.

Then, there are _irregular_ plurals like "`fish`" => "`fish`" and "`person`" => "`people`" and others like "`cactus`" => "`cacti`" or "`erratum`" => "`errata`".

However, you may need to override normal behavior. For instance, "`paper`" would normally turn into "`papers`" but you may need it to stay "`paper`".

This package is based on a javascript library that has encoded the core pluralization (and singularization) rules and exposed various functions to aid in maniuplating strings, including the ability to add special case rules (like the "`paper`" example).

Here are some examples to show the functionality:

Basic pluralization

```{r}
library(pluralize)

(plurals <- pluralize(c("snake", "window", "box", "boy", "lorry",
                        "potato", "knife")))
```

and the reverse:

```{r}
singularize(plurals)
```

ending "`o`":

```{r}
(plurals <- pluralize(c("echo", "embargo", "hero", "potato", "tomato",
                        "torpedo", "veto")))

singularize(plurals)
```

others ending "`o`":

```{r}
(plurals <- pluralize(c("auto", "kangaroo", "kilo", "memo", "photo", "piano",
                        "pimento", "pro", "solo", "soprano", "studio", "tattoo",
                        "video", "zoo")))

singularize(plurals)
```

Some special nouns:

```{r}
(plurals <- pluralize(c("knife", "leaf", "hoof", "life", "self", "elf")))

singularize(plurals)
```

Some irregular nouns:

```{r}
(plurals <- pluralize(c("fish", "sheep", "foot", "tooth", "goose",
                        "child", "man", "woman", "person", "mouse")))

singularize(plurals)
```

Again, you may want to do something special for certain words:

```{r}
add_plural_rule("corpus", "corpora")
add_plural_rule("formula", "formulae")
add_plural_rule("memoranda", "memorandums")

add_singular_rule("corpora", "corpus")
add_singular_rule("formulae", "formula")
add_singular_rule("memorandums", "memoranda")

(plurals <- pluralize(c("corpus", "formula", "memoranda")))

singularize(plurals)
```

Since this package is based on a javascript library -  [pluralize.js](https://github.com/blakeembrey/pluralize) by Blake Embrey - and uses the V8 package it won't be as lightning fast as a pure C/C++-backed package (it takes ~10 seconds to pluralize/singularize 10,000 words which is kinda horrible but sufficient for this project I'm working on), but it wouldn't take much to translate the rules built into `pluralize.js` over to C++.
